### 2017-04-06 paper/evaluation.tex
threats to validity section and lessons learned

>>>>

\subsection{Threats to Validity}

\Fix{Jean and Luis should write this. This is really important for an
  empirical study.  You need to undertand main sources of threat:
  internal, external, and construct.  Read this document for the
  basics: http://www.statsdirect.com/help/basics/validity.htm.  Read
  this document for an example:
  http://www.cin.ufpe.br/~damorim/publications/perez-etal-icst2017.pdf}

\subsection{Lessons Learned}

\Fix{Marcelo can write this...}
